Performance of two different ontological and data access methods

### 2014-07-06 cold2014/magnus.tex
Removed order list
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@736 43ef1190-90fd-4dd7-a769-d0121f02b80e
Small running experiment change
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@737 43ef1190-90fd-4dd7-a769-d0121f02b80e

The \emph{payload} is a dictionary of all the values to post to the
application.  After the request we saved the response which contained
the response time of a run. After each request we saved the run plus
the response time and wrote it to file on CSV format. To evaluate the
result we used the programming language R with the packages
\textsf{DoE.base}~\cite{DoEBase}, \textsf{FrF2}~\cite{FrF2} and
\textsf{BsMD}~\cite{BsMD}. R allowed us to parse the CSV files created
from the experiments and output them in two types of graphs.  A
similarity with all the experiments were that they all contained at
least the factors ontology, transmission and fuel type.

@@

If we take a look at the other factors, Fuel Consumption (FC) has
taken the top single factor spot on the list.  Each car has a lot of 
possible FC values to iterate
over. In CO, each car has an average amount of values of approximately
5.8. For VSO/COO it is 3.75.  This is the second highest overall after
emission. This by itself does not explain why FC is on the top of the
list, but when we take a look at when FC is queried it becomes more
clear. The order each specification is queried is shown below.  We can
see that FC comes right before E which means that it will have a
greater impact on the amount of values checked later.

 \begin{enumerate}
		\item Gears (G)
		\item Transmission (T)
		\item Fuel Consumption (FC)
		\item Emission (E)
		\item Doors (D)
		\item Total Weight (WT)
		\item Fuel Type (FT)
		\item Weight (W)
		\item Seating Capacity (SC)
\end{enumerate}

>>>>

After each request we saved the run plus
the response time and wrote it to file on CSV format. To evaluate the
result we used the programming language R with the packages
\textsf{DoE.base}~\cite{DoEBase}, \textsf{FrF2}~\cite{FrF2} and
\textsf{BsMD}~\cite{BsMD}. R allowed us to parse the CSV files created
from the experiments and output them in two types of graphs.

@@

If we take a look at the other factors, Fuel Consumption (FC) has
taken the top single factor spot on the list.  Each car has a lot of 
possible FC values to iterate
over. In CO, each car has an average amount of values of approximately
5.8. For VSO/COO it is 3.75.  This is the second highest overall after
emission. This by itself does not explain why FC is on the top of the
list, but when we take a look at when FC is queried it becomes more
clear. The order each specification is queried in this experiment 
from first to last is: G - T - FC - E - D - WT - FT - W - SC.  We can
see that FC comes right before E which means that it will have a
greater impact on the amount of values checked later.
